Describing the C-space of asynchronous periodic task using DIT

### 2013-07-29 dit-paper_ieee.tex
- title
small changes

			As explained in \cite{nemhauser1988integer}, a region of $\mathbb{N}_0^n$ such as the C-space can be described by a \emph{polytope}, or a list of parametric linear constraints (called the \emph{formulation}). The constraints must be conditions which can unequivocally decide if a point is included in the region or not. In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$\footnote{For a formulation in $\mathbb{N}^n$ rather than in $\mathbb{N}_0^n$, the following inequations can be added to the formulation \[ C_i \geqslant 1 \; \forall i \]}.\\

@@

As the FPDIT happened when all tasks were in the system, we know that the system will arrive in the exact same state one hyperperiod later ($t_d + H$)
We show (???) that we can restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the first periodic DIT exists. This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.\\

>>>>

			As explained in \cite{nemhauser1988integer}, a region of $\mathbb{N}_0^n$ such as the C-space can be described by a \emph{polytope}, or a list of parametric linear constraints (called the \emph{formulation}). The constraints must be conditions which can unequivocally decide if a point is included in the region or not. In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$ (For a formulation in $\mathbb{N}^n$, we can add $C_i \geqslant 1 \; \forall i$ to the formulation).\\

@@

As the FPDIT happens when all tasks are in the system, we know that the system will arrive in the exact same state one hyperperiod later ($t_d + H$). We can thus restrict the DBF test to intervals included in the interval $[t_d, t_d + H]$, if the FPDIT exists. This will always be a better interval than $[O_{max}, O_{max} + 2H]$ and if the first periodic DIT does not exist (which can be verified as explained in Section \ref{sct:FPDITexist}), the latter interval can be used.\\
